The Talking Heads Experiment

### 2015-04-17 preface/preface.tex
two \textsc in preface

\partref{part:2} of the book discusses what happened after the Talking Heads experiment. Our research went through various 
boom and bust cycles. In the good years there was money to hire new people and push the research forwards, but then 
bad years would come and the team disintegrated again due to lack of resources. This made progress less substantial than it
could have been but had the advantages that waves of new young people were given a chance to contribute. The first wave 
started working after the Talking Heads experiments were finished. At Sony CSL there was first exciting work by Pierre-Yves Oudeyer 
and Frederic Kaplan pursuing the origins of turn taking and symbol usage with the AIBO robots, thus exploring even earlier 
stages in the origins of language.

Thanks to the FP6 ECAgents project and the FP7 ALEAR projects of the European Commission, a new 
team could be formed around 2004, which included Joris Bleys, Joachim De Beule, Bart de Vylder, and Jelle Zuidema at the 
VUB in Brussels. Meanwhile, we got access through the Sony Computer Science Laboratory to the QRIO humanoid robots 
thanks to Masahiro Fujita and Hideki Shimomura. A new team formed in Paris which included Nancy Chang, Katya Gerasimova, Martin Loetzsch, 
Vanessa Micelli, Michael Spranger, Simon Pauw and Remi Van Trijp. I thank them all for major contributions to the experiments reported 
in the second part of the book. I also thank Stefano Nolfi for coordinating the ECAgents project with a firm hand 
and Manfred Hild and his team for creating the new humanoid MYON robot that we used in later experiments.

>>>>

\partref{part:2} of the book discusses what happened after the Talking Heads experiment. Our research went through various 
boom and bust cycles. In the good years there was money to hire new people and push the research forwards, but then 
bad years would come and the team disintegrated again due to lack of resources. This made progress less substantial than it
could have been but had the advantages that waves of new young people were given a chance to contribute. The first wave 
started working after the Talking Heads experiments were finished. At Sony CSL there was first exciting work by Pierre-Yves Oudeyer 
and Frederic Kaplan pursuing the origins of turn taking and symbol usage with the \textsc{aibo} robots, thus exploring even earlier 
stages in the origins of language.

Thanks to the FP6 ECAgents project and the FP7 ALEAR projects of the European Commission, a new 
team could be formed around 2004, which included Joris Bleys, Joachim De Beule, Bart de Vylder, and Jelle Zuidema at the 
VUB in Brussels. Meanwhile, we got access through the Sony Computer Science Laboratory to the QRIO humanoid robots 
thanks to Masahiro Fujita and Hideki Shimomura. A new team formed in Paris which included Nancy Chang, Katya Gerasimova, Martin Loetzsch, 
Vanessa Micelli, Michael Spranger, Simon Pauw and Remi Van Trijp. I thank them all for major contributions to the experiments reported 
in the second part of the book. I also thank Stefano Nolfi for coordinating the ECAgents project with a firm hand 
and Manfred Hild and his team for creating the new humanoid \textsc{myon} robot that we used in later experiments.
